### 2016-01-17 paper.tex
Add uncertainty formulas adapted from RVAT-Re-dep paper

Uncertainty was considered from a combination of systematic and random errors.
The random error was inferred from the sample standard deviation and the
systematic error from the sensor calibrations or datasheets. Combining both
sources of error, along with their propagation into quantities derived from
multiple measurements, followed the procedures outlined in Coleman and Steele
(2009) \cite{ColemanSteele}, described below.

An expanded uncertainty interval with 95\% confidence was computed for
$\lambda$, $C_P$, and $C_D$
\begin{equation}
    U_{95} = t_{95} u_c,
\end{equation}
where $t_{95}$ is the value from the Student-$t$ distribution for a 95\%
confidence interval and $u_c$ is the combined standard uncertainty. Combined
standard uncertainty for a given quantity $X$ is calculated by
\begin{equation}
    u_X^2 = s_X^2 + b_X^2,
\end{equation}
where $s_X$ is the sample standard deviation, calculated as the standard
deviation of the mean per turbine revolution, and $b_X$ is the systematic
uncertainty, computed by
\begin{equation}
    b_{X}^2 = \sum_{i=1}^J \left( \frac{\partial X}{\partial x_i} \right)^2
    b_{x_i}^2,
\end{equation}
where $x_i$ is a primitive quantity used to calculate $X$ (e.g. $T$, $\omega$,
and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
systematic uncertainty, estimated as half the value listed in
Table~\ref{tab-sensors}.

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
        \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ will be estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$.

From previous measurements of a similarly-sized vertical-axis turbine with the
same experimental setup, we expect expanded uncertainties for $\lambda$, $C_P$,
and $C_D$ to be approximately 0.008, 0.01, and 0.02, respectively, at a tow
speed $U_\infty = 1.0$ m/s. These values are well within the discrepancies
between previous measurements and predictions by CACTUS \cite{Michelen2014},
making the data from the experiments described here suitable for model validation.

>>>>

Both systematic and random errors were combined to calculate experimental
uncertainty. The random error was inferred from the sample standard deviation
(on a per-revolution basis) and the systematic error was estimated from the
sensor calibrations or datasheets. Combining both sources of error, along with
their propagation into quantities derived from multiple measurements, followed
the procedures outlined in Coleman and Steele \cite{ColemanSteele}, described
below.

For the mean rotor power and drag coefficients an expanded uncertainty interval
with 95\% confidence
\begin{equation}
    U_{95} = t_{95} u_c,
\end{equation}
was computed, where $t_{95}$ is the value from the Student-$t$ distribution for
a 95\% confidence interval and $u_c$ is the combined standard uncertainty.
Combined standard uncertainty for a given quantity $X$ is calculated by
\begin{equation}
    u_X^2 = s_{\bar{X}}^2 + b_X^2,
\end{equation}
where $s_{\bar{X}}$ is the sample standard deviation of the mean per turbine
revolution ($s_{\bar{X}} = s_X/\sqrt{N}$), and $b_X$ is the systematic
uncertainty, computed as
\begin{equation}
    b_{X}^2 = \sum_{i=1}^J \left( \frac{\partial X}{\partial x_i} \right)^2
    b_{x_i}^2,
\end{equation}
where $x_i$ is a primitive quantity used to calculate $X$ (e.g. $T$, $\omega$,
and $U_\infty$ for calculating $C_P$), and $b_{x_i}$ is the primitive quantity's
systematic uncertainty, estimated as half the value listed on the sensor
manufacturer's calibration or datasheet.

Selecting $t_{95}$ requires an estimate for degrees of freedom $\nu_X$, which
was obtained using the Welch--Satterthwaite formula
\begin{equation}
    \nu_X = \frac{\left(s_X^2 + \sum_{k=1}^M b_k^2 \right)^2} {s_X^4/\nu_{s_X} +
    \sum_{k=1}^M b_k^4/\nu_{b_k}},
\end{equation}
where $\nu_{s_X}$ is the number of degrees of freedom associated with $s_X$ and
$\nu_{b_k}$ is the number of degrees of freedom associated with $b_k$.
$\nu_{s_X}$ is assumed to be $(N-1)$, where $N$ is the number of independent
samples (or turbine revolutions). $\nu_{b_k}$ was estimated as
\begin{equation}
    \nu_{b_k} = \frac{1}{2} \left( \frac{\Delta b_k}{b_k} \right)^{-2},
\end{equation}
where the quantity in parentheses is the relative uncertainty of $b_k$, assumed
to be 0.25.
